Duration Analysis for Non-Expressive performances

### 2020-05-19 material/analysis/stim_n/duration.Rmd
add comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Duration - Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

#### Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

@@

#### Distribution plot
```{r duration_dis, fig.width = 12, echo = FALSE}
p_duration_dis <- ggplot(dt_duration[EighthNote == "Yes"], aes(x = normDu)) +
  geom_histogram(binwidth=.1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Non-Expression")
p_duration_dis
```

>>>>

---
title: 'Duration Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

#### Sequence plot
- Right wrap: Subject Number

```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

@@

#### Distribution plot
- Right wrap: Trial Number
- Upper wrap: Subject Number

```{r duration_dis, fig.width = 12, echo = FALSE}
p_duration_dis <- ggplot(dt_duration[EighthNote == "Yes"], aes(x = normDu)) +
  geom_histogram(binwidth=.1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Non-Expression")
p_duration_dis
```
